MT @HanBaldwin: Fightin OOVs in German \#twitter

### 2013-08-01 darmstadt_gscl_2013/article_twitter_normalization.tex
statistics updated

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``objective limitedness of MRD''\label{table:mrd}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    regular German words & 7.88 & 8.85 &  & \\
    compounds & 1.22 & 2.42 &  & \\
    abbreviations & 4.12 & 4.91 &  & \\
    interjections & 5.93 & 4.47 &  & \\
    person names & 4.79 & 6.45 &  & \\
    geographic locations & 1.51 & 2.53 &  & \\
    company names & 2.26 & 2.8 &  & \\
    product names & 2.08 & 2.49 &  & \\
    newly coined terms & 1.22 & 1.24 &  & \\
    loanwords & 3.72 & 4.05 &  & \\
    foreign words & 11.68 & 14 &  & \\\hline
    {\bfseries total} & 46.41 & 54.21 &  & \\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

Similarly to class \ref{dict}, we subdivided the group of misspellings
into the following subgroups:
\begin{enumerate}
  \item insertion;
  \item deletion;
  \item substitution;
\end{enumerate}
according to the kind of operation which led to a particular spelling
mistake. The statistics on distribution of these subgroups is shown in
Table \ref{table:spell}.
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``unintended sloppiness of users' input''\label{table:spell}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    insertion &  &  &  & \\
    deletion &  &  &  & \\
    substitution &  &  &  & \\\hline
    {\bfseries total} &  &  &  & \\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``stylistic specifics of text genre''}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}} & %
    \multicolumn{2}{c}{\texttt{hunspell}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    hashtags &  &  &  & \\
    @-tokens &  &  &  & \\
    links &  &  &  & \\
    smileys &  &  &  & \\
    slang &  &  &  & \\\hline
    {\bfseries total} &  &  &  & \\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

>>>>

dict           3.49
compound       4.55
abbr           3.44
inj            4.29
ne:person      3.47
ne:geo         1.88
ne:company     3.01
ne:product     3.23
neologism      2.38
loan           2.87
fw             10.91

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``objective limitedness of MRD''\label{table:mrd}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    regular German words & 7.82 & 8.78 & 2.8 & 3.49\\
    compounds & 1.21 & 2.42 & 2.51 & 4.55\\
    abbreviations & 3.98 & 4.77 & 3.27 & 3.44\\
    interjections & 5.95 & 4.54 & 5.58 & 4.29\\
    person names & 4.73 & 6.41 & 2.32 & 3.47\\
    geographic locations & 1.5 & 2.53 & 1.16 & 1.88\\
    company names & 2.27 & 2.84 & 4.35 & 3.01\\
    product names & 2.13 & 2.57 & 2.45 & 3.23\\
    newly coined terms & 1.35 & 1.31 & 3.33 & 2.38\\
    loanwords & 3.68 & 4.03 & 3.29 & 2.87\\
    foreign words & 11.5 & 13.76 &  9.57 & 10.91\\\hline
    {\bfseries total} & 46.12 & 53.96 & 40.63 & 43.52\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

Similarly to class \ref{dict}, we subdivided the class ``Unintended
sloppiness of users' input'' into the following subgroups:
\begin{enumerate}
  \item insertion;
  \item deletion;
  \item substitution;
\end{enumerate}
according to the kind of operation which led to a particular spelling
mistake. In cases when multiple different operations were involved
simultaneously, we explicitly marked each of these operations in our
data. You can see the statistics on distribution of these subgroups in
Table \ref{table:spell}.

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``unintended sloppiness of users' input''\label{table:spell}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    insertion & 0.49 & 1 & 0.18 & 0.34 \\
    deletion & 8.44 & 6.38 & 6.52 & 5.27 \\
    substitution & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
    {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

As it is clear from the table, deletions are by far the most common
type of spelling mistakes. This results on the one hand from
deliberate or unintended omissions of characters made by users but an
even more common source of these ill-formed words is automatic
truncation of messages made by Twitter.

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Stylistic specifics of text genre''}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    hashtags & 7.35 & 6.18 & 13.06 & 10.59\\
    @-tokens & 13.02 & 20.23 & 16.19 & 21.91\\
    links & 2.43 & 0.4 & 4.89 & 6.07\\
    smileys & 2 & 0.73 & 6.88 & 1.2\\
    slang & 16.22 & 5.27 & 6.94 & 4.77\\\hline
    {\bfseries total} & 41.02 & 32.81 & 47.96 & 44.54\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}
